% \newgeometry{lmargin=3cm, rmargin=3cm, tmargin=2.5cm, bmargin=2cm}
\pagestyle{plain}
\lhead[{}{}]       {{}{}}
\rhead[{}{}]       {{}{}}
\pagenumbering{gobble}

\begin{small}
\noindent \textsc{This whitepaper provides an initial summary of certain technical and business essentials underlying the Vega protocol. This document is expected to evolve over time, as the project proceeds. The Vega team may post modifications, revisions and/or updated drafts from time to time, including before, during, and after the creation of any tokens, and whilst network(s) based on the Vega protocol (`Vega Networks') are in operation.}

\textsc{This document sets forth a description of the Vega protocol, reference software implementation, and potential Vega Networks. This includes descriptions of the protocol itself, `smart products', and the use of tokens such as the proposed Vega Token. This document is provided for information purposes only and is not a binding legal agreement. Any sale or other offering of Vega Tokens would be governed by separate Terms \& Conditions. In the event of conflict between applicable Terms \& Conditions and this document, the Terms \& Conditions govern.}
 
\textsc{This whitepaper is not an offering document or prospectus, and is not intended to provide the basis of any investment decision or contract.}\par
\end{small}

\subsubsection*{Legal disclaimer}
\begin{scriptsize}
As of the date of publication, the Vega team have no plans to launch any public Vega Networks, and Vega Tokens are a proposed token with no known potential uses outside of Vega Networks, and no such use is intended. This document does not constitute advice nor a recommendation by the Vega team, its officers, directors, managers, employees, agents, advisers or consultants, or any other person to any recipient of this document on the merits of purchasing, otherwise acquiring, or holding Vega Tokens or any other cryptocurrency or token. The purchase and holding of cryptocurrencies and tokens carries substantial risks and may involve special risks that could lead to a loss of all or a substantial portion of any money invested. Do not purchase tokens unless you are prepared to lose the entire amount allocated to the purchase. 

Vega Tokens, if and when they are created and made available, should not be acquired for speculative or investment purposes with the expectation of making a profit or immediate re-sale. They should be acquired only if you fully understand the intended functionality of the Vega Tokens, and you intend to use the Vega Tokens for those purposes only, and it is legal for you to do so. No promises of future utility or performance or value are or will be made with respect to Vega Tokens, including no promise any Vega Networks will be launched, no promise of inherent value, no promise of any payments, and no guarantee that Vega Tokens will hold any particular value.
 
Vega Tokens are not designed and will not be structured or sold as securities. Vega Tokens will hold no rights and confer no interests in the equity of the Vega business or any future Vega Networks. Vega Tokens are designed and intended for future use on public Vega Networks that may be created using the Vega protocol, for the purposes of trading and governance transactions, or for the operation of a node. Proceeds of any sale of Vega Tokens may be spent freely by Vega for any purpose, including but not limited to the development of its business and underlying technological infrastructure, absent any conditions set out in this document.
 
This whitepaper is not a prospectus or disclosure document and is not an offer to sell, nor the solicitation of any offer to buy any investment or financial instrument or other product in any jurisdiction and should not be treated or relied upon as one. Any distribution of this whitepaper must be of the complete document including the cover page and this disclaimer and the accompanying boilerplate in their entirety.

All information in this document that is forward looking is speculative in nature and may change in response to numerous outside forces, including technological innovations, regulatory factors, and/or currency fluctuations, including but not limited to the market value of cryptocurrencies.

This whitepaper is for information purposes only and will be subject to change. The Vega team cannot guarantee the accuracy of the statements made or conclusions reached in this whitepaper. The Vega team does not make and expressly disclaims all representations and warranties (whether express or implied by statute or otherwise) whatsoever, including but not limited to: any representations or warranties relating to merchantability, fitness for a particular purpose, suitability, wage, title or non-infringement; that the contents of this document are accurate and free from any errors; and that such contents do not infringe any third party rights.

The Vega business, Vega team, and operators of any Vega Networks shall have no liability for damages of any kind arising out of the use, reference to or reliance on the contents of this whitepaper, even if advised of the possibility of such damages arising. 

This whitepaper includes references to third party data and industry publications. The Vega team believes that the information reproduced in this whitepaper is accurate and that the estimates and assumptions contained herein are reasonable. However, there are no assurances as to the accuracy or completeness of this data. The information from third party sources contained herein has been obtained from sources believed to be reliable; however, there are no assurances as to the accuracy or completeness of any included information. Although the data is believed to be reliable, the Vega team has not independently verified any of the information or data from third party sources referred to in this whitepaper or ascertained the underlying assumptions relied upon by such sources.

Please note that Vega is in the process of undertaking a legal and regulatory analysis of the functionality of the protocol, proposed Vega Tokens, and the operation of its business. Following the conclusion of this analysis, the Vega team may decide to amend the intended functionality of Vega Tokens in order to ensure compliance with any legal or regulatory requirements to which it is subject, which may affect the utility, fungibility, or any other properties of Vega Tokens.

Any Vega Tokens could be impacted by regulatory action, including potential restrictions on the ownership, use, or possession of such tokens. Regulators or other competent authorities may demand that the mechanics of the Vega Tokens be altered, entirely or in part. Vega may revise the Vega protocol or Vega Token mechanics to comply with regulatory requirements or other governmental or business obligations. Nevertheless, Vega believes it has taken all commercially reasonable steps to ensure that the design of Vega Tokens is proper and in compliance with currently considered regulations as far as reasonably possible. 

No regulatory authority has examined or approved any of the information set out in this whitepaper. The publication, distribution or dissemination of this whitepaper does not imply compliance with applicable laws or regulatory requirements.

\vspace{1em}\noindent \textbf{This entire document is~~\copyright~\the\year, Gobalsky Labs Ltd. All rights reserved.}\par
\end{scriptsize}
% \restoregeometry
